Tight Bounds for Online Balanced Graph Partitioning

### 2020-05-08 paper/disc20clustering.tex
Consistency

\maciek{TODOs: "requests between nodes" to "requests to pair of nodes"}

@@

\subsection{Model.}

@@

\subsection{Our Contributions.}
We provide an improved lower bound 
of $\Omega(k\cdot\ell)$ on the competitive ratio of any online deterministic online algorithm 
even in the learning model;
the best known lower bound so far was $\Omega(k)$,
even for a more general model~\cite{repartition-disc}.
We also present an asymptotically optimal, 
$O(k\cdot \ell)$-competitive algorithm
for the learning model.
For the repartitioning model, we present  
an asymptotically optimal,
$\Theta(\ell)$ algorithm for $k=3$, improving the best known upper bound 
so far $O(\ell^2)$~\cite{repartition-disc}.
Then, we present a strictly $6$-competitive algorithm for $k=2$ that improves upon previous $7$-competitive algorithm with $O(\ell^2)$ additive constant.
%
The overview of known results is in Table~\ref{tab:overview}.

@@

\section{Preliminaries.}
\label{sec:prelim}

@@

\subsection{Lower bound.}

@@

\subsection{Upper bound.}
\label{sec:ppl}

@@

\subsection{Improved algorithm for Online Rematching}
\label{sec:k2}

@@

\textbf{The charging Scheme.}
Consider two  pairs that share a same node, 
i.e.~\emph{intersecting pairs},
and the set of requests that causes the collocation of both pairs,
at some  times during  $[1,m]$.
%i.e.~the entire duration of the sequence.
Observe that \OPT must pay a non-zero cost
for these requests over the entire $\sigma$,
since it cannot have both pairs initially collocated.
%More precisely,
%OPT  pays a total cost at least
%	$\min{ \{ 2\lambda, \lambda+\alpha, 2\alpha \} }$ for, respectively,
%	serving requests to both pairs remotely,
%	serving requests to one pair remotely and collocating the other,
%	or collocating both pairs. 
%
%for serving (some of) these requests remotely or (and) collocating (one of) the pairs,
%regardless of its choices.
%Then the cost per pair, in particular the cost w.r.t.~$\{u,v\}$, is
%$\mathit{OPT} (\sigma_{\{u,v\}}) \geq c_{R_t} / 2$.
%
However,
we can charge the whole cost to \OPT only the first time \RM collocates a pair,
and not at any consequent time when \RM collocates it a second time.
Otherwise,
 \OPT is possibly charged for a same cost repeatedly.
For this reason,
we charge \OPT a cost inflicted by a pair,
if and only if  \OPT incurs the cost some time since the last time \RM separated the pair.
%%

@@

\section{Distributed implementation.}
The algorithm PPL from Section~\ref{sec:ppl} can be distributed
similarly to the approach in~\cite{sigmetrics19_partitioning}.
The algorithm for $k=2$ from Section~\ref{sec:k2} performs only local communication for each request: counters are kept on the clusters and updated locally, and each migration concerns only two clusters.
\medskip

@@

\begin{comment}
	\section{Bounding the cost of a single reconfiguration of components}

>>>>

@@

\subsection{Model}

@@

\subsection{Our Contributions}
We provide an improved lower bound 
of $\Omega(k\cdot\ell)$ on the competitive ratio of any online deterministic online algorithm 
even in the learning model;
the best known lower bound so far was $\Omega(k)$,
even for a more general model~\cite{repartition-disc}.
We also present an asymptotically optimal, 
$O(k\cdot \ell)$-competitive algorithm
for the learning model.
For the repartitioning model, we present  
an asymptotically optimal,
$\Theta(\ell)$ algorithm for $k=3$, improving the best known upper bound 
so far $O(\ell^2)$~\cite{repartition-disc}.
Then, we present a strictly $6$-competitive algorithm for $k=2$ that improves upon previous $7$-competitive algorithm with $O(\ell^2)$ additive constant.
%
The overview of known results is in Table~\ref{tab:overview}.

@@

\section{Preliminaries}
\label{sec:prelim}

@@

\subsection{Lower Bound}

@@

\subsection{Upper Bound}
\label{sec:ppl}

@@

\subsection{Improved Algorithm for Online Rematching}
\label{sec:k2}

@@

\textbf{The charging scheme.}
Consider two  pairs that share a same node, 
i.e.~\emph{intersecting pairs},
and the set of requests that causes the collocation of both pairs,
at some  times during  $[1,m]$.
%i.e.~the entire duration of the sequence.
Observe that \OPT must pay a non-zero cost
for these requests over the entire $\sigma$,
since it cannot have both pairs initially collocated.
%More precisely,
%OPT  pays a total cost at least
%	$\min{ \{ 2\lambda, \lambda+\alpha, 2\alpha \} }$ for, respectively,
%	serving requests to both pairs remotely,
%	serving requests to one pair remotely and collocating the other,
%	or collocating both pairs. 
%
%for serving (some of) these requests remotely or (and) collocating (one of) the pairs,
%regardless of its choices.
%Then the cost per pair, in particular the cost w.r.t.~$\{u,v\}$, is
%$\mathit{OPT} (\sigma_{\{u,v\}}) \geq c_{R_t} / 2$.
%
However,
we can charge the whole cost to \OPT only the first time \RM collocates a pair,
and not at any consequent time when \RM collocates it a second time.
Otherwise,
 \OPT is possibly charged for a same cost repeatedly.
For this reason,
we charge \OPT a cost inflicted by a pair,
if and only if  \OPT incurs the cost some time since the last time \RM separated the pair.
%%

@@

\section{Distributed Implementation}
The algorithm PPL from Section~\ref{sec:ppl} can be distributed
similarly to the approach in~\cite{sigmetrics19_partitioning}.
The algorithm for $k=2$ from Section~\ref{sec:k2} performs only local communication for each request: counters are kept on the clusters and updated locally, and each migration concerns only two clusters.
\medskip

@@

	\section{Bounding the cost of a single reconfiguration of components}
